### 2010-03-23 papers/icfp-2010-desc/paper_idesc.tex
Desc@ICFP: introduce \DConst when moving Desc to a type former presentation. Transfered from IDesc and avoid redundancy.

In the alternative presentation, we go further and present all our
codes as quotations of standard type-formers. This presentation is
shown in Figure~\ref{fig:type-former-desc}. The reader will notice the
introduction of $\DProd{}{}$ that overlaps with $\DSigma{}{}$. Unlike
$\DSigma{}{}$, $\DProd{}{}$ is first-order, hence amenable to a
definitional treatment. \note{We could replace $\DUnit$ by $\DConst$
  here, instead of doing it in the following section. This is also a
  story about being first-order, so that would make sense, isn't it?}

@@

\[\stk{
\begin{array}{ll}
\stk{
\data \Desc : \Set \where \\
\;\;\begin{array}{@{}l@{\::\:\:}l@{\quad}l}
    \DId            & \Desc                                   \\
    \DUnit          & \Desc                                   \\
    \DProd{}{}      & \PI{\V{D}, \V{D'}}{\Desc} \Desc         \\
    \DSigma         & \PI{\V{S}}{\Set} \PIS{S \To \Desc} \Desc \\
    \DPi            & \PI{\V{S}}{\Set} \PIS{S \To \Desc} \Desc 
\end{array}
}
\vspace{0.2in}
\\
\stk{
\descop{\_\:}{} : \Desc \To \Set \To \Set \\
\begin{array}{@{}l@{\:=\:\:}ll}
\descop{\DId}{X}          &  X                                           \\
\descop{\DUnit}{X}        &  \Unit                                       \\
\descop{\DProd{D}{D'}}{X} &  \TIMES{\descop{D}{X}}{\descop{D'}{X}}       \\
\descop{\DSigma{S}{D}}{X} &  \SIGMA{\V{s}}{S} \descop{D\: s}{X}                \\
\descop{\DPi{S}{D}}{X}    &  \PI{\V{s}}{S} \descop{D\: s}{X}            
\end{array}
}
\end{array}
}\]

@@

The resulting code of $\IDesc$ is presented in
Figure~\ref{fig:idesc}. The reader will notice that we have also
replaced $\DUnit$ by a more general $\DConst$ code. Whereas $\DUnit$
was interpreted as the unit set, $\DConst{X}$ is interpreted as $X$,
for any $\Bhab{X}{\Set}$. Extensionally, $\DConst{X}$ and
$\DSigma{X}{\DUnit}$ are equivalent. However, $\DConst$ is more
succinct. More importantly, $\DConst$ is \emph{first-order}, unlike
its equivalent encoding. From a definitional perspective, we are
giving more opportunities to the type-system, hence reducing the
burden on the programmer.

>>>>

In the alternative presentation, we go further and present all our
codes as quotations of standard type-formers. This presentation is
shown in Figure~\ref{fig:type-former-desc}. The reader will notice
that we replace $\DUnit$ by a more general $\DConst$ code. Whereas
$\DUnit$ was interpreted as the unit set, $\DConst{X}$ is interpreted
as $X$, for any $\Bhab{X}{\Set}$. Extensionally, $\DConst{X}$ and
$\DSigma{X}{\DUnit}$ are equivalent. However, $\DConst$ is more
succinct. More importantly, $\DConst$ is \emph{first-order}, unlike
its equivalent encoding. From a definitional perspective, we are
giving more opportunities to the type-system, hence reducing the
burden on the programmer. For the same reason, we introduce
$\DProd{}{}$ that overlaps with $\DSigma{}{}$.

@@

\[\stk{
\begin{array}{ll}
\stk{
\data \Desc : \Set \where                                      \\
\;\;\begin{array}{@{}l@{\::\:\:}l@{\quad}l}
    \DId            & \Desc                                    \\
    \DConst{}       & \Set \To \Desc                           \\
    \DProd{}{}      & \PI{\V{D}, \V{D'}}{\Desc} \Desc          \\
    \DSigma         & \PI{\V{S}}{\Set} \PIS{S \To \Desc} \Desc \\
    \DPi            & \PI{\V{S}}{\Set} \PIS{S \To \Desc} \Desc 
\end{array}
}
\vspace{0.2in}
\\
\stk{
\descop{\_\:}{} : \Desc \To \Set \To \Set \\
\begin{array}{@{}l@{\:=\:\:}ll}
\descop{\DId}{X}          &  X                                           \\
\descop{\DConst{Z}}{X}    &  Z                                           \\
\descop{\DProd{D}{D'}}{X} &  \TIMES{\descop{D}{X}}{\descop{D'}{X}}       \\
\descop{\DSigma{S}{D}}{X} &  \SIGMA{\V{s}}{S} \descop{D\: s}{X}          \\
\descop{\DPi{S}{D}}{X}    &  \PI{\V{s}}{S} \descop{D\: s}{X}            
\end{array}
}
\end{array}
}\]

@@

The resulting code of $\IDesc$ is presented in
Figure~\ref{fig:idesc}.
